Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
MAJOR code cleaning of intro, inductive lem

\section{Introduction}

Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations. We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$. It may well be that $\Gamma \backslash \bh$ is not comapact. Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$. We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[Chapters 7-9]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.

In order to answer this question, we translate the seemingly analytic question into the algebraic category, using a generalization of the GAGA principle. That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of categories between orbifold curves and log stacky curves over $\BC$. Hence, for the remainder of the paper, we will work in the algebraic category.

Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is well known that the sheaf $\Omega_X,$ with associated divisor $K_X$ determines the {\bf canonical map} $\pi:X \rightarrow \BP_k^{g-1}.$ Then, the {\bf canonical ring}, is defined as
\begin{align*}
	R(X,K_X) = \bigoplus_{n \geq 0} H^0(X,nK_X),
\end{align*}

@@

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
$\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
for signatures with $g = 0$.
\end{thm}
\todo{Say that this follows immediately from the three theorems for the special cases.}
Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite[Section III.4]{neves:halfcan}.

The remainder of the paper will be primarily devoted to proving Theorem ~\ref{thm:general_generators_relations}. The idea of the proof will be to induct on the order and number of elliptic points. To this end, we first review important background in Section ~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we develop various inductive tools. In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section ~\ref{sec:further-questions}, we pose several questions for future research.

@@

\section{Background}
\label{sec:background}
\todo{Reference independence of base field}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on grobner bases
	\item Notation $h^0 = \dim H^0$.
	\item Why we have these fractions $\frac{e_i-1}{2e_i}$ and why $e_i$ must be odd.
\end{enumerate}

@@

\section{Inductive Lemmata}
\label{sec:induction}
First we present the general inductive lemmata that will be applied
for all genera.  We offer various inductive lemmata that will allow us to add fractional point $\frac{\alpha}{\beta}P$ to a $\mathbf{Q}$ divisor $D$ of $X$ and describe the new generators and relations of $R_{D+p}$ not in $R_D$.  Next, we provide a method specific to the case of stacky canonical divisors with no log component, which under certain conditions allows us to transfer information about the generators and relations of the half canonical ring of a stacky curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$ where each $e_i\in \{e_i', e_i'+2\}$.

However, before we can answer these general lemmata, it is useful to prove a nice result about minimal generation of ideals of relations:
\todo{Include one of the following, if the first one, include a remark for quotient}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}

%
%\begin{lem}
%\label{lem:minimal_quadratic_2}
%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
%generated in degree 1 that are equipped with monomial ordering $\prec$.
 %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
%\[
	%\begin{tikzcd}
	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%Further suppose that $I'$ is generated over $I$ by elements $f_1,
%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
%is of the form $y_i$.  Then, the elements $f_i$ determine minimal
%generators for $I'$ over $I$.
%\end{lem}
%
%\begin{proof}
%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
%\]
%\[
	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
%\]
%
%
%\noindent
%determines map of rings, no longer necessarily graded. 
%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
%\[
	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
%\]
%so
%\[
	%\dim_k (I'/I)_2=j.
%\]
%This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%
%
%\begin{rem}
%\label{rem:minimal_quadratic_trivial_case}
%It will be useful to use lemma \ref{lem:minimal_quadratic} in the
%case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
%are $k$-minimal generators for $I'$ (over the trivial base vector
%space).  
%\end{rem}

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.  Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).   The proofs of these lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.  Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, x_m$ all with $\ord_P(u) =0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)=1$. Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}
In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
\end{itemize}
\end{lem}

\begin{proof}
Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
These can be chosen generically to not have a zero at $P$ \todo{
check that we can actually do this, or eliminate if it turns out to
be unnecessary}.

@@

\noindent
be the non-negative best lower approximation of $\frac{
\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
each other and $(R_D)_d$, so by degree considerations, they span
$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.

@@

\noindent
Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees.  
Generically choose some $y_i \in(R_{
D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
\[
	-\ord_P(y_i)= \max(c_j:d_j=1)
\]

@@

Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
\beta}$ not a best lower approximation.  Then choose
best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
this we can deduce that 
\[
	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
\]

>>>>

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup
of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by
fractional linear transformations. We can then consider the
orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the
case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a
Riemann Surface over $\BC$. It may well be that $\Gamma \backslash
\bh$ is not compact. Defining $\Delta$ as the divisor of cusps
associated to $\Gamma$, we can form a space $\Gamma \backslash
\bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with
associated {\bf divisor of cusps} $\Delta$.

We can now consider the
{\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In
this paper, for general $\Gamma$, we sharply bound the degree of
the generators and relations for $M(\Gamma).$ This was already
answered in \cite[Chapters 7-9]{vzb:stacky} in the case that
$M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is,
when $\Gamma$ has no odd weight modular forms, and we extend this
to all Fuchsian subgroups $\Gamma$. In order to answer this
question, we translate the seemingly analytic question into the
algebraic category, using a generalization of the GAGA principle.
That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an
equivalence of categories between orbifold curves and log stacky
curves over $\BC$. Hence, for the remainder of the paper, we will
work in the algebraic category. Let $X$ be a smooth algebraic
curve over $k$ of genus $g$. It is well known that the sheaf $\Omega
_X,$ with associated divisor $K_X$ determines the {\bf canonical map
} $\pi:X \rightarrow \BP_k^{g - 1}.$ Then, the {\bf canonical ring},
is defined as
\begin{align*}
	R(X,K_X) = \bigoplus_{n \geq 0} H^0(X,nK_X),
\end{align*}

@@

Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
much more general setting, generalizing Petri's theorem in many
directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
$(\sx,\Delta)$ denote a tame separably rooted curve over a
field $k$ so that $X$ is the coarse space of $\sx$, as defined in
\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$,
be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx +
\Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log
spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
The central object of study in this paper is the {\bf log spin
canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
$\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g - 1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
for signatures with $g = 0$.
\end{thm}

\todo{Say that this follows immediately from the three theorems for the special cases.}

Note that in the course of the proof of Theorem
~\ref{thm:g_0_generators_relations} we will not merely obtain
bounds on the degrees of the generators and relations. In fact, if
the genus $g = 0$ or $g = 1$, the proof yields an explicit system
of generators and the initial ideal of relations. While in the
genus $g \geq 2$ case, the proof does not always yield an explicit
system of generators and relations, if the halfcanonical divisor
$\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',
0, X)$ a log spin curve, and a system of generators and relations for
$ \halfcan'$ is known, then our proof provides an inductive
procedure for determining the generators and initial ideal of
relations for $ \halfcan$. In fact, such a system of generators and
relations are known for $\halfcan'$ in many cases, as detailed in
Neves ~\cite[ Section III.4]{neves:halfcan}.

The remainder of the paper will be primarily devoted to proving
Theorem ~\ref{thm:general_generators_relations}. The idea of the
proof will be to induct on the order and number of elliptic points.
To this end, we first review important background in Section
~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we
develop various inductive tools. In Sections ~\ref{sec:g_high},
~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem
~\ref{thm:general_generators_relations} in the cases that the genus
$g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section
~\ref{sec:further-questions}, we pose several questions for future
research.

@@

\section{Background}
\label{sec:background}
\todo{Reference independence of base field}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on grobner bases
	\item Notation $h^0 = \dim H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
\end{enumerate}

@@

\section{Inductive Lemmata}
\label{sec:induction}
First we present the general inductive Lemmata that will be applied
for all genera. We offer various inductive Lemmata that will allow
us to add fractional point $\frac{\alpha}{\beta}P$ to a $\BQ$
 divisor $D$ of $X$ and describe the new generators and relations
of $R_{D+p}$ not in $R_D$. Next, we provide a method specific to
the case of stacky canonical divisors with no log component, which
under certain conditions allows us to transfer information about
the generators and relations of the half canonical ring of a stacky
curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a
stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$
where each $e_i\in \{e_i', e_i' + 2\}$.

However, before we can answer these general Lemmata, it is useful
to prove a nice result about minimal generation of ideals of
relations.

\todo{Include one of the following, if the first one, include a 
remark for quotient}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1, \ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}

%
%\begin{lem}
%\label{lem:minimal_quadratic_2}
%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
%generated in degree 1 that are equipped with monomial ordering $\prec$.
 %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
%\[
	%\begin{tikzcd}
	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%Further suppose that $I'$ is generated over $I$ by elements $f_1,
%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
%is of the form $y_i$. Then, the elements $f_i$ determine minimal
%generators for $I'$ over $I$.
%\end{lem}
%
%\begin{proof}
%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
%\]
%\[
	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
%\]
%
%
%\noindent
%determines map of rings, no longer necessarily graded. 
%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
%\[
	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
%\]
%so
%\[
	%\dim_k (I'/I)_2=j.
%\]
%This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%
%
%\begin{rem}
%\label{rem:minimal_quadratic_trivial_case}
%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
%are $k$-minimal generators for $I'$ (over the trivial base vector
%space). 
%\end{rem}

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).  The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, x_m$ all with $\ord_P(u) = 0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)= 1$. Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0<\frac{c_1}{d_1}<\ldots<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n- 1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i + 1} + 1)}: 1\le i =\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}

In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
	and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
	\frac{\alpha}{\beta} \rfloor} + 1}$ as shown above minimally
generates $I'$.
\end{itemize}
\end{lem}

\begin{proof}
Observe that $u_D, x_1, \ldots, x_m$ each of which has no pole at $P$.
These can be chosen generically to not have a zero at $P$ \todo{
check that we can actually do this, or eliminate if it turns out to
be unnecessary}.

@@

\noindent
be the non-negative best lower approximation of $\frac{
\alpha}{\beta}$. Note that elements of $H^0(X, dD')$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$. A set of these one for each pole degree 1 to $\lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
each other and $(R_D)_d$, so by degree considerations, they span
$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.

@@

\noindent
Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Generically choose some $y_i \in(R_{
D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i = 1$ then 
\[
	-\ord_P(y_i)= \max(c_j:d_j = 1)
\]

@@

Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
\beta}$ not a best lower approximation. Then choose
best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
maximal; since $c<c_{i + 1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$. From
this we can deduce that 
\[
	c_i +(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
\]
